An open reproducible framework for the study of the iterated prisoner's dilemma

### 2016-04-01 tex/paper.tex
Resizing images to reduce page count.

\begin{figure}[!hbtp]
	\begin{subfigure}{.5\textwidth}
		\centering
		\includegraphics[width=\textwidth]{../img/demo_tournament.pdf}
		\caption{The results from a simple tournament.}
		\label{fig:demo_tournament}
	\end{subfigure}
	\begin{subfigure}{.5\textwidth}
		\centering
		\includegraphics[width=\textwidth]{../img/stewart_tournament.pdf}
		\caption{The results from \cite{Stewart2012}.}
		\label{fig:stewart_tournament}
	\end{subfigure}
	\caption{Summary plots produced by the library.}
\end{figure}

@@

\begin{figure}[!hbtp]
	\begin{subfigure}{.5\textwidth}
		\centering
		\includegraphics[width=\textwidth]{../img/outline_of_library.pdf}
		\caption{An overview of the source code.}
		\label{fig:overview}
	\end{subfigure}
	\begin{subfigure}{.5\textwidth}
		\centering
		\includegraphics[width=\textwidth]{../img/number_of_strategies_with_arima_projection.pdf}
		\caption{The number of strategies included in the library}
		\label{fig:number_of_strategies_against_date}
	\end{subfigure}
	\caption{An overview of the library.}
\end{figure}

@@

\begin{figure}[!hbtp]
	\centering
	\includegraphics[width=.9\textwidth]{../img/tournament.pdf}
	\caption{Results from the library tournament (2016-03-31)}
	\label{fig:tournament}
\end{figure}

>>>>

\begin{figure}[!hbtp]
	\begin{subfigure}{.5\textwidth}
		\centering
		\includegraphics[width=.75\textwidth]{../img/demo_tournament.pdf}
		\caption{The results from a simple tournament.}
		\label{fig:demo_tournament}
	\end{subfigure}
	\begin{subfigure}{.5\textwidth}
		\centering
		\includegraphics[width=.75\textwidth]{../img/stewart_tournament.pdf}
		\caption{The results from \cite{Stewart2012}.}
		\label{fig:stewart_tournament}
	\end{subfigure}
	\caption{Summary plots produced by the library.}
\end{figure}

@@

\begin{figure}[!hbtp]
	\begin{subfigure}{.5\textwidth}
		\centering
		\includegraphics[width=.75\textwidth]{../img/outline_of_library.pdf}
		\caption{An overview of the source code.}
		\label{fig:overview}
	\end{subfigure}
	\begin{subfigure}{.5\textwidth}
		\centering
		\includegraphics[width=.9\textwidth]{../img/number_of_strategies_with_arima_projection.pdf}
		\caption{The number of strategies included in the library}
		\label{fig:number_of_strategies_against_date}
	\end{subfigure}
	\caption{An overview of the library.}
\end{figure}

@@

\begin{figure}[!hbtp]
	\centering
	\includegraphics[width=.75\textwidth]{../img/tournament.pdf}
	\caption{Results from the library tournament (2016-03-31)}
	\label{fig:tournament}
\end{figure}
